Project Notes - Installability

### 2021-06-24 StateOfPractice/Peter-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Edits to slides to remove from Peter's slides parts that are Ao specific
updated LBM domain expert presentation

\usepackage{booktabs}
\usepackage{bibentry}
\usepackage[round, authoryear]{natbib}
\bibliographystyle{plainnat}

@@

\begin{frame}
\frametitle{Scope}

[Ao put your scope figure here.  Peter, you can delete this slide.]

@@

[Peter and Ao, please put your list here, with hyperlinks if possible.  You can use
columns to make it all fit on one slide.]

@@

[Peter, please list your commonalities here; Ao, we'll use a scope slide
instead]

@@

[Peter, please list your variabilities, with their associated parameters of
variation here; Ao, you can delete this slide]

>>>>

\usepackage{multicol}
\usepackage{booktabs}
\usepackage{bibentry}
\usepackage[round, authoryear]{natbib}
\bibliographystyle{plainnat}

@@

@@

\begin{multicols}{2}	
	\bi
			\item \href{https://ludwig.epcc.ed.ac.uk/}{Ludwig}
			\item \href{http://espressomd.org/wordpress/}{ESPResSo}
			\item \href{https://palabos.unige.ch/}{Palabos}
			\item \href{https://www.openlb.net/}{OpenLB}
			\item \href{https://github.com/aharwood2/LUMA/}{LUMA}
			\item \href{https://pypi.org/project/pylbm/}{pyLBM}
			\item \href{https://www.scd.stfc.ac.uk/Pages/DL_MESO.aspx}{DL\_MESO (LBE)}
			\item \href{https://www.walberla.net}{waLBerla}
			\item \href{http://sailfish.us.edu.pl/}{Sailfish}
			\item \href{https://github.com/maxlevesque/laboetie}{laboetie}
			\item \href{https://docs.tclb.io/}{TCLB}
			\item \href{http://mechsys.nongnu.org/}{MechSys}
			\item \href{https://github.com/Olllom/lettuce}{lettuce}
			\item \href{https://github.com/espressopp/espressopp}{ESPResSo++} 
			\item \href{https://github.com/carlosrosales/mplabs}{MP-LABS}		
			\item \href{http://sunlightlb.sourceforge.net/}{SunlightLB}
			\item \href{http://ccs.chem.ucl.ac.uk/lb3d}{LB3D} - 			
			\href{https://www.sciencedirect.com/science/article/pii/S0010465517301017}{paper}
			\item \href{https://code.google.com/archive/p/limbes/}{LIMBES}
			\item \href{http://faculty.fiu.edu/~sukopm/LBnD_Prime/LBnD_Prime.html}{LB2D-Prime}	
			\item \href{https://github.com/UCL/hemelb}{HemeLB} 
			\item \href{https://pypi.org/project/lbmpy/}{lbmpy}	
			\item \href{http://faculty.fiu.edu/~sukopm/LBnD_Prime/LBnD_Prime.html}{LB3D-Prime}	
			\item \href{https://github.com/UCL/LatBo.jl}{LatBo.jl}
	\ei
\end{multicols}

@@

\bi
	\item Lattice - discretized domain within a boundary
	\item Collision operator (The Bhatnagar-Gross-Krook Collision Operator is common)
	\item Probability density function
	\item Equilibrium distribution function
	\item Boltzmann transport equation
\ei

@@

\bi
\item May use parallel processing
\item Different equilibrium distribution functions
\item Coefficients for equilibrium distribution function (based on velocity directions)
\item Lattice dimensions (1D, 2D, 3D)
\item Varied velocity directions, partially based on dimensions 
\item Collision operators (SRT, TRT, MRT, BGK)
\item Collision vs collision-free transport equations
\item Number of fluid that can be modeled simultaneously
\item Fluid parameters (Reynolds Num., density, viscosity, etc.)
\item Lattice boundary (reflective or non-reflective)
\ei
